\section{Introduction}

%%% Motivation

\hspace{\parindent} When developing mobile applications, the question of a shared codebase for both Android and iOS platforms often arises. Writing two applications with similar features in distinct programming languages seem to be a waste of time. As such, many cross-platform frameworks have been created to compensate this drawback. Relying on different programming languages from JavaScript to Dart and Go, all share the promise of sparing some precious development time by using a single codebase for both Android and iOS platforms. But what are the actual advantages and drawbacks of such frameworks, compared to writing directly native applications? \\

This project aims to evaluate some of the most famous cross-platform frameworks through various criteria. These are tested by writing for each a simple and similar application with basic but mandatory features. Frameworks can then be compared to each other, on criteria ranging from ease of integration of existing code to the UI library capabilities.\\
The report discusses the development process for those applications, the issues encountered and their severity level, and finishes with the evaluation of the frameworks.\\
NativeScript is the starting point of those evaluations as the popcoins app\footnote{\url{https://github.com/dedis/popcoins}} developed at DEDIS already depends on this cross-platform framework. React Native, Flutter, Go Mobile, Xamarin and Ionic frameworks are then explored. Finally, a summary of the important information is given and a discussion comparing frameworks altogether takes place.